\begin{dance}
  {The Reel of the 51st Confusion}
  {R32 3/3L}{32-bar reel for three couples in a three-couple longwise set}

  \phrase{1}{8}{
    1st couple set, cast off two places and lead up, finishing back to back
    facing first corners. 2nd couple step up on bars 3-4.
  }

  \phrase{9}{16}{
    1st couple set to first corners and turn with right hand halfway with them.
    first corners give left hands in the middle and 1st couple and first corners
    balance in line; first corners turn with left hand one and a quarter times
    to end up back to back facing second corners.
  }

  \phrase{17}{24}{
    Repeat with first and second corners. At the last left-hand turn, finish on
    the lines with 1st, 2nd and 3rd women improper in 1st, 2nd and 3rd position
    and 2nd, 3rd and 1st men improper in 1st, 2nd and 3rd position.
  }

  \phrase{25}{32}{
    All dance six hands round and back.
  }

  \repeatfromnewpos

  Devised by \deviser{Anne Lanvin, Corentin Lefèvre, Isabelle Herlant, Louise
    Baltera, Nicolas “Niols” Jeannerod and Victor Lanvin} on August 8th, 2021.
  This dance is a variation on one of the most popular Scottish country dances,
  {\em The Reel of the 51st Division}.

  Note: Remember the person that is at the left of your partner from your point
  of view: First, third and fifth times, you will start dancing with your
  partner on your original lines; Second, fourth and sixth times, you will start
  dancing with that other person on the opposite lines.

  Recommended music: \tune{The Sober Piper}, by \composer{Anne Lanvin}.
  Alternatively, one can use one of the tunes for {\em The Reel of the 51st
    Division}: {\em The Drunken Piper}, by {\em Alex McLeod}.
\end{dance}
