\begin{dance}
  {Praha Matka Měst}
  {M32 3/3L}{Medley of 16-bar strathspey and 16-bar reel\\
    for three couples in a three-couple longwise set}

  On second chord, 2nd and 3rd couples cross.

  Strathspey

  \phrase{1}{8}{
    1st couple set advancing and turn both hands, dance down the middle and turn
    halfway with both hands to face down in Promenade hold. 2nd couple step up
    on bars 5-6. 2nd and 3rd couples join in on bar 8.
  }

  \phrase{9}{16}{
    2nd, 1st and 3rd couples dance an Allemande down the dance. On bars 15-16,
    1st couple stays in the middle and set advancing to face first corners in
    third corner position.
  }

  Reel

  \phrase{17}{24}{
    1st couple dance corners pass and turn and cast away: Same as corners pass
    and turn, except that corners turn halfway right hand and cast away to
    opposite positions. On bars 23-24, 1st couple slows down to finish in the
    middle on own sides in Poussette hold; 3rd man curves to stay in the middle
    on own side; 3rd woman joins in in Poussette hold.
  }

  \phrase{25}{32}{
    1st and 3rd couples dance Poussette and petronella: Same five first bars as
    the Poussette. On bar 6, 3rd and 1st couples dance a quarter. On bars 7-8,
    3rd and 1st couples dance a petronella turn to opposite lines, finishing
    with 2nd couple in first position, and 3rd and 1st couples improper in
    second and third position.
  }

  \repeatfromnewpos

  Devised by \deviser{Nicolas “Niols” Jeannerod} in April 2019.

  Music by \composer{Nicolas “Niols” Jeannerod}.
\end{dance}
